Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-13 doc/slides/hong+eisner.TLT13.slides.tex
Edited the slides some more.

\subsection{Link Grammars Intro}
\frame{\frametitle{Link Grammars}
  \includegraphics[width=\linewidth]{linkgrammar_example1.png}\footnote{These figures were clipped from the orginal Link Grammar paper: \\``Parsing English with a Link Grammar'' by Sleator and Temperley}
}

\frame{\frametitle{Link Grammars}
  \includegraphics[width=\linewidth]{linkgrammar_example2.png}
}

\frame{\frametitle{Link Grammars}
  \includegraphics[width=\linewidth]{linkgrammar_example3.png}
}

\frame{\frametitle{Link Grammars: Same Example Parse Again}
  \begin{figure}
    \begin{dependency}[edge style={-}]
	  \begin{deptext}
	    - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	    the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  \end{deptext}
	  \depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	  \depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	  \depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	  \depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	  \depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	  \depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	  \deproot[edge above, thick, edge style = {red}]{2}{W}
	  \deproot[edge above, thick, edge style = {red}]{7}{WV}
	  \deproot[edge above, thick, edge style = {red}]{10}{X}
	  \depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	  \depedge[edge above, thick, edge style = {red}]{6}{5}{E}
    \end{dependency}
    \caption*{Link Parse of a sentence from Penn Tree Bank}
  \end{figure}
}

\frame{\frametitle{Link Grammars: Converting into a Directed Acyclic Graph Again}
  \begin{figure}
    \begin{dependency}
	  \begin{deptext}
	    - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	    the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  \end{deptext}
	  \depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	  \depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	  \depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	  \depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	  \depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	  \depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	  \deproot[edge above, thick, edge style = {red}]{2}{W}
	  \deproot[edge above, thick, edge style = {red}]{7}{WV}
	  \deproot[edge above, thick, edge style = {red}]{10}{X}
	  \depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	  \depedge[edge above, thick, edge style = {red}]{6}{5}{E}
    \end{dependency}

@@

\frame{\frametitle{Link Results: Subject-Verb links are backwards}
\begin{itemize}
      %\item Different dependency formalisms disagree on whether a clause is headed by the aux verb or the main verb.
  \item The Link Grammar seems to be inconsistent about whether the auxiliary verb or the main verb is the head of a clause. 
  \item Sometimes the governing verb links to the auxilliary, and sometimes to the main, depending on the type of clause. 
  \item But the governing verb usually links to the subject when there is one.
  \item So this makes the subject a consistent choice to make the head of a clause.
\end{itemize}

@@

\begin{center}
  To fix this, we could edit the link grammar, link parses, or the ILP. %\\ Our technique is only as useful as the input given.
\end{center}

    %Question: Which do we pick?
    %Answer: Neither! We actually pick the subject as the head of the clause! 
    %Question: Why??
    %Answer:
    %    The LG folks seem to be inconsistent within their grammar about whether the aux verb or the main verb is the head of a clause. 
    %        Sometimes the governing verb links to aux, and sometimes to main, depending on the type of clause.
    %    But the governing verb usually links to the subject when there is one!
    %    Therefore, the subject ends up being a consistent choice for the head of the clause.  We get governing_verb --> subject --> aux --> main as our annotation scheme.
    %Question: Couldn't this be fixed?
    %Answer: Of course it could.  You could edit the link grammar or the link parses or the ILP.  Our technique is only as useful as the input you give it ...  
}

>>>>

\subsection{Link Grammars Intro}
\frame{\frametitle{Link Grammars: How They Work}
  \includegraphics[width=\linewidth]{linkgrammar_example1.png}\footnote{These figures were clipped from the orginal Link Grammar paper: \\``Parsing English with a Link Grammar'' by Sleator and Temperley}
}

\frame{\frametitle{Link Grammars: How They Work}
  \includegraphics[width=\linewidth]{linkgrammar_example2.png}
}

\frame{\frametitle{Link Grammars: How They Work}
  \includegraphics[width=\linewidth]{linkgrammar_example3.png}
}

\frame{\frametitle{Link Grammars: Same Example Parse From Before Again}
  \begin{figure}
    \begin{dependency}[edge style={-}]
	  \begin{deptext}
	    - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	    the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  \end{deptext}
	  \depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	  \depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	  \depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	  \depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	  \depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	  \depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	  \deproot[edge above, thick, edge style = {red}]{2}{W}
	  \deproot[edge above, thick, edge style = {red}]{7}{WV}
	  \deproot[edge above, thick, edge style = {red}]{10}{X}
	  \depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	  \depedge[edge above, thick, edge style = {red}]{6}{5}{E}
    \end{dependency}
    \caption*{Link Parse of a sentence from Penn Tree Bank}
  \end{figure}
}

\frame{\frametitle{Link Grammars: Converting into a Directed Acyclic Graph}
  \begin{figure}
    \begin{dependency}
	  \begin{deptext}
	    - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	    the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  \end{deptext}
	  \depedge[edge above, thick, edge style = {red}]{2}{3}{S}
	  \depedge[edge above, thick, edge style = {red}]{3}{6}{I}
	  \depedge[edge above, thick, edge style = {red}]{2}{1}{D}
	  \depedge[edge above, thick, edge style = {red}]{7}{8}{MV}
	  \depedge[edge above, thick, edge style = {red}]{6}{7}{P}
	  \depedge[edge above, thick, edge style = {red}]{8}{9}{J}
	  \deproot[edge above, thick, edge style = {red}]{2}{W}
	  \deproot[edge above, thick, edge style = {red}]{7}{WV}
	  \deproot[edge above, thick, edge style = {red}]{10}{X}
	  \depedge[edge above, thick, edge style = {red}]{6}{4}{E}
	  \depedge[edge above, thick, edge style = {red}]{6}{5}{E}
    \end{dependency}

@@

\frame{\frametitle{Link Results: Subject-Verb links are backwards}
\begin{itemize}
      %\item Different dependency formalisms disagree on whether a clause is headed by the aux verb or the main verb.
  \uncover<1->{\item The Link Grammar seems to be inconsistent about whether the auxiliary verb or the main verb is the head of a clause. }
  \uncover<2->{\item Sometimes the governing verb links to the auxilliary, and sometimes to the main, depending on the type of clause. }
  \uncover<3->{\item But the governing verb usually links to the subject when there is one.}
  \uncover<4->{\item So this makes the subject a consistent choice to make the head of a clause.}
\end{itemize}

@@

\uncover<5->{
\begin{center}
  To fix this, we could edit the link grammar, link parses, or the ILP. %\\ Our technique is only as useful as the input given.
\end{center}
}
    %Question: Which do we pick?
    %Answer: Neither! We actually pick the subject as the head of the clause! 
    %Question: Why??
    %Answer:
    %    The LG folks seem to be inconsistent within their grammar about whether the aux verb or the main verb is the head of a clause. 
    %        Sometimes the governing verb links to aux, and sometimes to main, depending on the type of clause.
    %    But the governing verb usually links to the subject when there is one!
    %    Therefore, the subject ends up being a consistent choice for the head of the clause.  We get governing_verb --> subject --> aux --> main as our annotation scheme.
    %Question: Couldn't this be fixed?
    %Answer: Of course it could.  You could edit the link grammar or the link parses or the ILP.  Our technique is only as useful as the input you give it ...  
}
